Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-09-16 main.tex
hpfem
minor corrections

We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the \emph{Poincar\'e--Friedrichs inequality} with exponent $p \in [1,\infty]$
if there exists a constant $C_{{\rm PF},\Omega,p} \geq 0$ such that the following holds:
for every vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists $u \in W^{1,p}(\Omega)$
such that $\nabla u = \bff$ and 
\begin{align}\label{math:inequalitypf:gradient}
    \| u \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm PF},\Omega,p} 
    \| \bff \|_{L^{p}(\Omega)}
    .
\end{align}
Since $\Omega$ is connected, this is equivalent to  
\begin{align*}
    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm PF},\Omega,p} 
    \| \nabla u \|_{L^{p}(\Omega)},
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    .
\end{align*}
We call $C_{{\rm PF},\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
\\

@@

    C_{{\rm P},\Omega,p} \leq 2 C_{{\rm PF},\Omega,p}.
In the special case $p=2$, taking the average is an orthogonal projection, and so this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$. Hence $C_{{\rm P},\Omega,2} = C_{{\rm PF},\Omega,2}$. 

@@

    C_{{\rm P},\Omega,p} \leq 2^{|2/p-1|} C_{{\rm PF},\Omega,p}.

@@

There is yet another characterization of the Poincar\'e--Friedrichs inequality that we like to point out. 
We define the potential 
\begin{align*}
    \Phi( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)},
    \quad 
    \forall 
    \bff \in \nabla W^{1,p}(\Omega)
    .
\end{align*}
If there is a Poincar\'e--Friedrichs constant, then by definition
\begin{align*}
    \| \Phi(\bff) \|_{L^{p}(\Omega)} \leq C_{{\rm PF},\Omega,p} \| \bff \|_{L^{p}(\Omega)},
\end{align*}
and this inequality is sharp by definition of $\Phi$ provided that $C_{{\rm PF},\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
However, $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ is generally a nonlinear operator for $p \neq 2$. 
Consequently, any \textit{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
\begin{align*}
    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
    \frac{ \| \Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
    \leq 
    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
    \frac{ \| \overline\Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
    .
\end{align*}
A natural choice is the linear operator $\Phi_{{\rm P}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that satisfies 
\begin{align*}
    \Phi_{{\rm P}}( \nabla u ) = u - u_{\Omega},
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    .
\end{align*}
Its operator norm is just the optimal Poincar\'e constant $C_{{\rm P},\Omega,p}$.
\\

@@

We know optimal Poincar\'e--Friedrichs constants over convex domains~(\cite[Theorem~1.1]{ferone2012remark}\cite[Theorem~1.1]{esposito2013poincare}): 
when $1 < p < \infty$, one can show that 
\begin{align}\label{math:esposito:pf}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm PF},{\rm EFNT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where $C_{{\rm PF},{\rm EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
\begin{align*}
    C_{{\rm PF},{\rm EFNT},p}
    :=
    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
    .
\end{align*}
Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
\begin{align}\label{math:esposito:poincare}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    2^{|1-\frac 2 p|}C_{{\rm PF},{\rm EFNT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    .
\end{align}
When $p=1$, then the optimal Poincar\'e constant $1/2$ also bounds the Poincar\'e--Friedrichs constant:
\begin{align}\label{math:l1estimate}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{1}(\Omega)}
    \leq 
    \frac{ \diam(\Omega) }{2}
    \| \nabla u \|_{L^{1}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,1}(\Omega)
    .
\end{align}
When $p=\infty$, since convex domains are Lipschitz domains, Rademacher's theorem leads to 
\begin{align}\label{math:lipschitzestimate}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{\infty}(\Omega)}
    \leq 
    \diam(\Omega)
    \| \nabla u \|_{L^{\infty}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,\infty}(\Omega)
    .
\end{align}

@@

\begin{remark}
    % The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case. 
    Any estimate for the Poincar\'e--Friedrichs constant implies an estimate for the Poincar\'e constant, via~\eqref{math:p_vs_pf}. 
    Let us compare the estimate $C_{{\rm P},{\rm CW},p}$ for the Poincar\'e constant
    with the estimate obtained from the Poincar\'e--Friedrichs constant $C_{{\rm PF},{\rm EFNT},p}$. 
    In the case $2 \leq p$, 
    \begin{align*}
        2^{1-\frac 2 p}
        C_{{\rm PF},{\rm EFNT},p}
        =
        \frac{ 2^{1-\frac 2 p} }{2}
        \frac{ \sin(\pi/p) }{ \pi/p }
        \frac{ 1 }{ \sqrt[p]{p-1} }
        \leq 
        4^{-\frac 1 p}
        \leq
        C_{{\rm P},{\rm CW},p} 
        .
    \end{align*}
    In the case $2 \geq p$, 
    \begin{align*}
        2^{\frac 2 p - 1}
        C_{{\rm PF},{\rm EFNT},p}
        =
        \frac{ 2^{\frac 2 p - 1} }{2}
        \frac{ \sin(\pi/p) }{ \pi/p }
        \frac{ 1 }{ \sqrt[p]{p-1} }
        \leq
        \frac{ 2^{\frac 2 p-1} }{2}
        &
        =
        2^{\frac 2 p - 2}
        \\&
        =
        4^{\frac 1 p - 1}
        \leq
        C_{{\rm P},{\rm CW},p} 
%         % 
%         .
%         4^{\frac 1 p}
%         \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} \cdot 2 }
%         =
%         4^{\frac 1 p}
%         \frac{ p \sin(\pi/p) }{ 4\pi \sqrt[p]{p-1} }
%         \leq 
%         \frac{1}{2}
        .
    \end{align*}
    It follows that \eqref{math:esposito:poincare} is generally a tighter estimate than \eqref{math:chuawheeden} for $1 < p < \infty$.
    % DONE: what exactly is the limit as p -> 1 ? It converges to 1.
    % DONT: insert the original inequality by chua and Wheeden
    % DONE: chua wheeden upper bound is not optimal!
    % DONE: Theorem 1.2 in Chua Wheeden 
% DONT: Keep ?
%     In the limit as $p$ goes to $1$, the factor $C_{{\rm PF},{\rm EFNT},p}$ converges to $1/2$,
%     which is the optimal Poincar\'e--Friedrichs constant and also the optimal factor in the Poincar\'e inequality \eqref{math:acostaduran}
%     \begin{align*}
%         \| u - u_{\Omega} \|_{L^{1}(\Omega)}
%         \leq 
%         \frac{1}{2}
%         \diam(\Omega)
%         \| \nabla u \|_{L^{1}(\Omega)}
%         ,
%         \quad
%         \forall 
%         u \in W^{1,1}(\Omega)
%         .
%     \end{align*}
%     In the limit as $p$ goes to infinity, the factor $C_{{\rm PF},{\rm EFNT},p}$ converges to $1/2$, 
%     which implies the Poincar\'e inequality 
%     \begin{align*}
%         \| u - u_{\Omega} \|_{L^{\infty}(\Omega)}
%         \leq 
%         \diam(\Omega)
%         \| \nabla u \|_{L^{\infty}(\Omega)}
%         ,
%         \quad
%         \forall 
%         u \in W^{1,\infty}(\Omega)
%         %
%     \end{align*}
%     because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. % DONT: cite 
%     % DONT: review this entire result 
\end{remark}

@@

\begin{lemma}\label{lemma:poincarefriedrichsoverfacepatch}
    Suppose that $T, T'$ are two $n$-simplices whose intersection is a common face $F := T_1 \cap T_2$. 
    Write $U := T_1 \cup T_2$. 
    Then 
    \begin{align*}
        \min\limits_{ c \in \bbR }
        \| u - c \|_{L^{p}(U)}
        &
        \leq 
        2 C_{{\rm PF},{\rm EFNT},p}
        \max\left( 
            \frac{ \vol(T_1) }{ \vol(T_2) }
            ,
            \frac{ \vol(T_2) }{ \vol(T_1) }
        \right)^{\frac 1 p}
        \\&\qquad\qquad 
        \cdot 
        \max\left( \diam(T_1), \diam(T_2) \right)
        \| \nabla u \|_{L^{p}(U)}
        \\&
        \leq 
        2 C_{{\rm PF},{\rm EFNT},p}
        \rho(\calT)^{\frac 1 p}
        \max\left( \diam(T_1), \diam(T_2) \right)
        \| \nabla u \|_{L^{p}(U)}
        .
    \end{align*}
    for any $u \in W^{1,p}(\Omega)$ with $p \in [1,\infty]$.
\end{lemma}
% \begin{remark}
%     The result is sharp when $T_1$ and $T_2$ have equal volume and diameter, and that $U$ is not necessarily convex. 
% \end{remark}
\begin{proof}
    Let $\hat T_1$ be the reference $n$-simplex whose vertices $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v_n = e_n$ are the origin and the $n$ canonical unit vectors. 
    We let $\hat T_2$ be the $n$-simplex whose vertices are $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v'_n = -e_n$. 
    Let $\hat U := \hat T_1 \cup \hat T_2$, which is convex. 
    We fix affine diffeomorphisms $\varphi_1 : \hat T_1 \rightarrow T_1$ and $\varphi_2 : \hat T_2 \rightarrow T_2$
    which map the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F$.
    Note that these affine transformations define a bi-Lipschitz mapping $\varphi : \hat U \rightarrow U$.

    Suppose that $u \in W^{1,p}(U)$. Then $\hat u := u \circ \varphi \in W^{1,p}(\hat U)$. 
    We observe 
    \begin{align*}
        \| \nabla \hat u \|_{L^{p}(\hat U)}^{p}
        &=
        \| \nabla \hat u \|_{L^{p}(\hat T_1)}^{p}
        +
        \| \nabla \hat u \|_{L^{p}(\hat T_2)}^{p}
        ,
        \\
        \| \nabla \hat u \|_{L^{p}(\hat T_1)}^{p}
        &\leq 
        |\det(\Jacobian \varphi_1^{-1})|
        \cdot \| \Jacobian \varphi_1 \|^{p}
        \cdot 
        \| \nabla u \|_{L^{p}(T_1)}^{p}
        ,
        \\
        \| \nabla \hat u \|_{L^{p}(\hat T_2)}^{p}
        &\leq 
        |\det(\Jacobian \varphi_2^{-1})|
        \cdot \| \Jacobian \varphi_2 \|^{p}
        \cdot 
        \| \nabla u \|_{L^{p}(T_2)}^{p}
%         \\&
%         \leq 
%         \max\left( 
%             |\det(\Jacobian \varphi_1)|^{-1} \cdot \| \Jacobian \varphi_1 \|^{p}
%             ,
%             |\det(\Jacobian \varphi_2)|^{-1} \cdot \| \Jacobian \varphi_2 \|^{p}
%         \right)
%         \| \nabla u \|_{L^{p}(U)}^{p}
        .
    \end{align*}
    Hence 
    \begin{align*}
        \| \nabla \hat u \|_{L^{p}(\hat U)}
        &\leq 
        \max\left( 
            |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \| \Jacobian \varphi_1 \|
            ,
            |\det(\Jacobian \varphi_2)|^{-\frac 1 p} \| \Jacobian \varphi_2 \|
        \right)
        \| \nabla u \|_{L^{p}(U)}
        .
    \end{align*}
    Notice that $\hat U$ has diameter $2$. 
    There exists $\hat w \in W^{1,p}(\hat U)$ such that $\nabla \hat w = \nabla \hat u$ and 
    \begin{align*}
        \| \hat w \|_{L^{p}(\hat U)}
        \leq 
        2 C_{{\rm PF},{\rm EFNT},p}
        \| \nabla \hat u \|_{L^{p}(\hat U)}
        .
    \end{align*}
    Next, setting $w := \hat w \circ \varphi^{-1}$, we find $\nabla w = \nabla u$ and 
    \begin{align*}
        \| w \|_{L^{p}(U)}
        \leq 
        \max\left( 
            |\det(\Jacobian \varphi_1)|
            ,
            |\det(\Jacobian \varphi_2)|
        \right)^{\frac 1 p}
        \| \hat w \|_{L^{p}(\hat U)}
        .
    \end{align*}
    % DONE: that abbreviation is to close to the Jacobian / total derivative 
    Abbreviate $D := \max\left( \diam(T_1), \diam(T_2) \right)$. In combination, 
    \begin{align*}
        \| w \|_{L^{p}(U)}
        &\leq 
        2 C_{{\rm PF},{\rm EFNT},p}
        \max\left( 
            |\det(\Jacobian \varphi_1)|
            ,
            |\det(\Jacobian \varphi_2)|
        \right)^{\frac 1 p}
        \\&\qquad 
        \max\left( 
            |\det(\Jacobian \varphi_1)|^{-\frac 1 p} 
            ,
            |\det(\Jacobian \varphi_2)|^{-\frac 1 p} 
        \right)
        D
        \| \nabla u \|_{L^{p}(U)}
        \\&
        \leq 
        2 C_{{\rm PF},{\rm EFNT},p}
        \max\left( 
            |\det(\Jacobian \varphi_1)|
            ,
            |\det(\Jacobian \varphi_2)|
        \right)^{\frac 1 p}
        \\&\qquad 
        \min\left( 
            |\det(\Jacobian \varphi_1)|
            ,
            |\det(\Jacobian \varphi_2)| 
        \right)^{-\frac 1 p} 
        D
        \| \nabla u \|_{L^{p}(U)}
        \\&
        \leq 
        2 C_{{\rm PF},{\rm EFNT},p}
        \max\left( 
            \frac{ |\det(\Jacobian \varphi_1)| }{ |\det(\Jacobian \varphi_2)| }
            ,
            \frac{ |\det(\Jacobian \varphi_2)| }{ |\det(\Jacobian \varphi_1)| }
        \right)^{\frac 1 p}
        D
        \| \nabla u \|_{L^{p}(U)}
        \\&
        \leq 
        2 C_{{\rm PF},{\rm EFNT},p}
        \max\left( 
            \frac{ \vol(T_1) }{ \vol(T_2) }
            ,
            \frac{ \vol(T_2) }{ \vol(T_1) }
        \right)^{\frac 1 p}
        D
        \| \nabla u \|_{L^{p}(U)}
        .
    \end{align*}
    This gives the desired result. 
\end{proof}

@@

        C_{{\rm PF},T_{m},F_{m},p} \| \nabla u - \nabla w'_{m} \|_{L^{p}(T_{m})}.
        C_{{\rm PF},T_{m},F_{m},p} \| \nabla u      \|_{L^{p}(T_{m})} 
        C_{{\rm PF},T_{m},F_{m},p} \| \nabla w'_{m} \|_{L^{p}(T_{m})} 

@@

        C_{{\rm PF},T_{m},F_{m},p} 

@@

        % C_{{\rm PF},T_{m},F_{m},p} 

@@

>>>>

We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the \emph{Poincar\'e--Friedrichs inequality} with exponent $p \in [1,\infty]$
if there exists a constant $C_{\PF,\Omega,p} \geq 0$ such that the following holds:
for every vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists $u \in W^{1,p}(\Omega)$
such that $\nabla u = \bff$ and 
\begin{align}\label{math:inequalitypf:gradient}
    \| u \|_{L^{p}(\Omega)}
    \leq 
    C_{\PF,\Omega,p} 
    \| \bff \|_{L^{p}(\Omega)}
    .
\end{align}
Since $\Omega$ is connected, this is equivalent to  
\begin{align*}
    \min_{ c \in \bbR } \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{\PF,\Omega,p} 
    \| \nabla u \|_{L^{p}(\Omega)},
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    .
\end{align*}
We call $C_{\PF,\Omega,p}$ the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
\\

@@

    C_{{\rm P},\Omega,p} \leq 2 C_{\PF,\Omega,p}.
In the special case $p=2$, taking the average is an orthogonal projection, and so this improves to $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $u \in L^{2}(\Omega)$. Hence $C_{{\rm P},\Omega,2} = C_{\PF,\Omega,2}$. 

@@

    C_{{\rm P},\Omega,p} \leq 2^{|2/p-1|} C_{\PF,\Omega,p}.

@@

There is yet another characterization of the Poincar\'e--Friedrichs inequality that we like to point out. 
We define the potential 
\begin{align*}
    \Phi( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)},
    \quad 
    \forall 
    \bff \in \nabla W^{1,p}(\Omega)
    .
\end{align*}
If there is a Poincar\'e--Friedrichs constant, then by definition
\begin{align*}
    \| \Phi(\bff) \|_{L^{p}(\Omega)} \leq C_{\PF,\Omega,p} \| \bff \|_{L^{p}(\Omega)},
\end{align*}
and this inequality is sharp by definition of $\Phi$ provided that $C_{\PF,\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
However, $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ is generally a nonlinear operator for $p \neq 2$. 
Consequently, any \textit{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
\begin{align*}
    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
    \frac{ \| \Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
    \leq 
    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
    \frac{ \| \overline\Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
    .
\end{align*}
A natural choice is the linear operator $\Phi_{{\rm P}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that satisfies 
\begin{align*}
    \Phi_{{\rm P}}( \nabla u ) = u - u_{\Omega},
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    .
\end{align*}
Its operator norm is just the optimal Poincar\'e constant $C_{{\rm P},\Omega,p}$.
\\

@@

We know optimal Poincar\'e--Friedrichs constants over convex domains~(\cite[Theorem~1.1]{ferone2012remark}\cite[Theorem~1.1]{esposito2013poincare}): 
when $1 < p < \infty$, one can show that 
\begin{align}\label{math:esposito:pf}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{\PF,{\rm EFNT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where $C_{\PF,{\rm EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
\begin{align*}
    C_{\PF,{\rm EFNT},p}
    :=
    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
    .
\end{align*}
Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
\begin{align}\label{math:esposito:poincare}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    2^{|1-\frac 2 p|}C_{\PF,{\rm EFNT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    .
\end{align}
When $p=1$, then the optimal Poincar\'e constant $1/2$ also bounds the Poincar\'e--Friedrichs constant:
\begin{align}\label{math:l1estimate}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{1}(\Omega)}
    \leq 
    \frac{ \diam(\Omega) }{2}
    \| \nabla u \|_{L^{1}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,1}(\Omega)
    .
\end{align}
When $p=\infty$, since convex domains are Lipschitz domains, Rademacher's theorem leads to 
\begin{align}\label{math:lipschitzestimate}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{\infty}(\Omega)}
    \leq 
    \diam(\Omega)
    \| \nabla u \|_{L^{\infty}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,\infty}(\Omega)
    .
\end{align}

@@

\begin{remark}
    % The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case. 
    Any estimate for the Poincar\'e--Friedrichs constant implies an estimate for the Poincar\'e constant, via~\eqref{math:p_vs_pf}. 
    Let us compare the estimate $C_{{\rm P},{\rm CW},p}$ for the Poincar\'e constant
    with the estimate obtained from the Poincar\'e--Friedrichs constant $C_{\PF,{\rm EFNT},p}$. 
    In the case $2 \leq p$, 
    \begin{align*}
        2^{1-\frac 2 p}
        C_{\PF,{\rm EFNT},p}
        =
        \frac{ 2^{1-\frac 2 p} }{2}
        \frac{ \sin(\pi/p) }{ \pi/p }
        \frac{ 1 }{ \sqrt[p]{p-1} }
        \leq 
        4^{-\frac 1 p}
        \leq
        C_{{\rm P},{\rm CW},p} 
        .
    \end{align*}
    In the case $2 \geq p$, 
    \begin{align*}
        2^{\frac 2 p - 1}
        C_{\PF,{\rm EFNT},p}
        =
        \frac{ 2^{\frac 2 p - 1} }{2}
        \frac{ \sin(\pi/p) }{ \pi/p }
        \frac{ 1 }{ \sqrt[p]{p-1} }
        \leq
        \frac{ 2^{\frac 2 p-1} }{2}
        &
        =
        2^{\frac 2 p - 2}
        \\&
        =
        4^{\frac 1 p - 1}
        \leq
        C_{{\rm P},{\rm CW},p} 
%         % 
%         .
%         4^{\frac 1 p}
%         \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} \cdot 2 }
%         =
%         4^{\frac 1 p}
%         \frac{ p \sin(\pi/p) }{ 4\pi \sqrt[p]{p-1} }
%         \leq 
%         \frac{1}{2}
        .
    \end{align*}
    It follows that \eqref{math:esposito:poincare} is generally a tighter estimate than \eqref{math:chuawheeden} for $1 < p < \infty$.
    % DONE: what exactly is the limit as p -> 1 ? It converges to 1.
    % DONT: insert the original inequality by chua and Wheeden
    % DONE: chua wheeden upper bound is not optimal!
    % DONE: Theorem 1.2 in Chua Wheeden 
% DONT: Keep ?
%     In the limit as $p$ goes to $1$, the factor $C_{\PF,{\rm EFNT},p}$ converges to $1/2$,
%     which is the optimal Poincar\'e--Friedrichs constant and also the optimal factor in the Poincar\'e inequality \eqref{math:acostaduran}
%     \begin{align*}
%         \| u - u_{\Omega} \|_{L^{1}(\Omega)}
%         \leq 
%         \frac{1}{2}
%         \diam(\Omega)
%         \| \nabla u \|_{L^{1}(\Omega)}
%         ,
%         \quad
%         \forall 
%         u \in W^{1,1}(\Omega)
%         .
%     \end{align*}
%     In the limit as $p$ goes to infinity, the factor $C_{\PF,{\rm EFNT},p}$ converges to $1/2$, 
%     which implies the Poincar\'e inequality 
%     \begin{align*}
%         \| u - u_{\Omega} \|_{L^{\infty}(\Omega)}
%         \leq 
%         \diam(\Omega)
%         \| \nabla u \|_{L^{\infty}(\Omega)}
%         ,
%         \quad
%         \forall 
%         u \in W^{1,\infty}(\Omega)
%         %
%     \end{align*}
%     because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. % DONT: cite 
%     % DONT: review this entire result 
\end{remark}

@@

\begin{lemma}\label{lemma:poincarefriedrichsoverfacepatch}
    Suppose that $T, T'$ are two $n$-simplices whose intersection is a common face $F := T_1 \cap T_2$. 
    Write $U := T_1 \cup T_2$. 
    Then 
    \begin{align*}
        \min\limits_{ c \in \bbR }
        \| u - c \|_{L^{p}(U)}
        &
        \leq 
        2 C_{\PF,{\rm EFNT},p}
        \max\left( 
            \frac{ \vol(T_1) }{ \vol(T_2) }
            ,
            \frac{ \vol(T_2) }{ \vol(T_1) }
        \right)^{\frac 1 p}
        \\&\qquad\qquad 
        \cdot 
        \max\left( \diam(T_1), \diam(T_2) \right)
        \| \nabla u \|_{L^{p}(U)}
        \\&
        \leq 
        2 C_{\PF,{\rm EFNT},p}
        \rho(\calT)^{\frac 1 p}
        \max\left( \diam(T_1), \diam(T_2) \right)
        \| \nabla u \|_{L^{p}(U)}
        .
    \end{align*}
    for any $u \in W^{1,p}(\Omega)$ with $p \in [1,\infty]$.
\end{lemma}
% \begin{remark}
%     The result is sharp when $T_1$ and $T_2$ have equal volume and diameter, and that $U$ is not necessarily convex. 
% \end{remark}
\begin{proof}
    Let $\hat T_1$ be the reference $n$-simplex whose vertices $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v_n = e_n$ are the origin and the $n$ canonical unit vectors. 
    We let $\hat T_2$ be the $n$-simplex whose vertices are $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v'_n = -e_n$. 
    Let $\hat U := \hat T_1 \cup \hat T_2$, which is convex. 
    We fix affine diffeomorphisms $\varphi_1 : \hat T_1 \rightarrow T_1$ and $\varphi_2 : \hat T_2 \rightarrow T_2$
    which map the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F$.
    Note that these affine transformations define a bi-Lipschitz mapping $\varphi : \hat U \rightarrow U$.

    Suppose that $u \in W^{1,p}(U)$. Then $\hat u := u \circ \varphi \in W^{1,p}(\hat U)$. 
    We observe 
    \begin{align*}
        \| \nabla \hat u \|_{L^{p}(\hat U)}^{p}
        &=
        \| \nabla \hat u \|_{L^{p}(\hat T_1)}^{p}
        +
        \| \nabla \hat u \|_{L^{p}(\hat T_2)}^{p}
        ,
        \\
        \| \nabla \hat u \|_{L^{p}(\hat T_1)}^{p}
        &\leq 
        |\det(\Jacobian \varphi_1^{-1})|
        \cdot \| \Jacobian \varphi_1 \|^{p}
        \cdot 
        \| \nabla u \|_{L^{p}(T_1)}^{p}
        ,
        \\
        \| \nabla \hat u \|_{L^{p}(\hat T_2)}^{p}
        &\leq 
        |\det(\Jacobian \varphi_2^{-1})|
        \cdot \| \Jacobian \varphi_2 \|^{p}
        \cdot 
        \| \nabla u \|_{L^{p}(T_2)}^{p}
%         \\&
%         \leq 
%         \max\left( 
%             |\det(\Jacobian \varphi_1)|^{-1} \cdot \| \Jacobian \varphi_1 \|^{p}
%             ,
%             |\det(\Jacobian \varphi_2)|^{-1} \cdot \| \Jacobian \varphi_2 \|^{p}
%         \right)
%         \| \nabla u \|_{L^{p}(U)}^{p}
        .
    \end{align*}
    Hence 
    \begin{align*}
        \| \nabla \hat u \|_{L^{p}(\hat U)}
        &\leq 
        \max\left( 
            |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \| \Jacobian \varphi_1 \|
            ,
            |\det(\Jacobian \varphi_2)|^{-\frac 1 p} \| \Jacobian \varphi_2 \|
        \right)
        \| \nabla u \|_{L^{p}(U)}
        .
    \end{align*}
    Notice that $\hat U$ has diameter $2$. 
    There exists $\hat w \in W^{1,p}(\hat U)$ such that $\nabla \hat w = \nabla \hat u$ and 
    \begin{align*}
        \| \hat w \|_{L^{p}(\hat U)}
        \leq 
        2 C_{\PF,{\rm EFNT},p}
        \| \nabla \hat u \|_{L^{p}(\hat U)}
        .
    \end{align*}
    Next, setting $w := \hat w \circ \varphi^{-1}$, we find $\nabla w = \nabla u$ and 
    \begin{align*}
        \| w \|_{L^{p}(U)}
        \leq 
        \max\left( 
            |\det(\Jacobian \varphi_1)|
            ,
            |\det(\Jacobian \varphi_2)|
        \right)^{\frac 1 p}
        \| \hat w \|_{L^{p}(\hat U)}
        .
    \end{align*}
    % DONE: that abbreviation is to close to the Jacobian / total derivative 
    Abbreviate $D := \max\left( \diam(T_1), \diam(T_2) \right)$. In combination, 
    \begin{align*}
        \| w \|_{L^{p}(U)}
        &\leq 
        2 C_{\PF,{\rm EFNT},p}
        \max\left( 
            |\det(\Jacobian \varphi_1)|
            ,
            |\det(\Jacobian \varphi_2)|
        \right)^{\frac 1 p}
        \\&\qquad 
        \max\left( 
            |\det(\Jacobian \varphi_1)|^{-\frac 1 p} 
            ,
            |\det(\Jacobian \varphi_2)|^{-\frac 1 p} 
        \right)
        D
        \| \nabla u \|_{L^{p}(U)}
        \\&
        \leq 
        2 C_{\PF,{\rm EFNT},p}
        \max\left( 
            |\det(\Jacobian \varphi_1)|
            ,
            |\det(\Jacobian \varphi_2)|
        \right)^{\frac 1 p}
        \\&\qquad 
        \min\left( 
            |\det(\Jacobian \varphi_1)|
            ,
            |\det(\Jacobian \varphi_2)| 
        \right)^{-\frac 1 p} 
        D
        \| \nabla u \|_{L^{p}(U)}
        \\&
        \leq 
        2 C_{\PF,{\rm EFNT},p}
        \max\left( 
            \frac{ |\det(\Jacobian \varphi_1)| }{ |\det(\Jacobian \varphi_2)| }
            ,
            \frac{ |\det(\Jacobian \varphi_2)| }{ |\det(\Jacobian \varphi_1)| }
        \right)^{\frac 1 p}
        D
        \| \nabla u \|_{L^{p}(U)}
        \\&
        \leq 
        2 C_{\PF,{\rm EFNT},p}
        \max\left( 
            \frac{ \vol(T_1) }{ \vol(T_2) }
            ,
            \frac{ \vol(T_2) }{ \vol(T_1) }
        \right)^{\frac 1 p}
        D
        \| \nabla u \|_{L^{p}(U)}
        .
    \end{align*}
    This gives the desired result. 
\end{proof}

@@

        C_{\PF,T_{m},F_{m},p} \| \nabla u - \nabla w'_{m} \|_{L^{p}(T_{m})}.
        C_{\PF,T_{m},F_{m},p} \| \nabla u      \|_{L^{p}(T_{m})} 
        C_{\PF,T_{m},F_{m},p} \| \nabla w'_{m} \|_{L^{p}(T_{m})} 

@@

        C_{\PF,T_{m},F_{m},p} 

@@

        % C_{\PF,T_{m},F_{m},p} 

@@

\subsection{Estimates for partial boundary conditions}
